Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-01-06 manuscript/manuscript.Rmd
Update manuscript.Rmd

Power transformation does not always

@@

>>>>

Power transformation does not always yield transformed variables that

@@

We make the following contributions:

-   We devise shift-sensitive versions of the Box-Cox and Yeo-Johnson transformation, including versions robust to outliers.

-   We define an empirical measure of the goodness of fit for detecting cases when power transformations fail to yield a normally distributed transformed feature.

-   We assess the effect of power transformations on the performance of machine learning models.
